Updates on the Exoplanet Orbit Database

### 2013-12-28 draft/ms.tex
Abbreviate related fields in table.

\tablecaption{Fields of Exoplanet Orbit Database}

@@

@@

BINARY\dotfill & Boolean & Star known ot be binary? & BINARYREF BINARYURL \\

@@

V\dotfill & Float & $V$ magnitude & VREF,VURL \\

@@

DIST\dotfill & & & DISTUPPER,DISTLOWER,UDIST,DISTREF,DISTURL \\
PAR\dotfill & Float & Parallax in mas & PARUPPER,PARLOWER,UPAR \\

@@

star & VSINIUPPER,VSINILOWER,UVSINI,VSINIREF,VSINIURL \\
GAMMA\dotfill & & & GAMMAUPPER,GAMMALOWER,UGAMMA,GAMMAREF,GAMMAURL \\

@@

PER\dotfill & Double & Orbital period in days & PERUPPER,PERLOWER,UPER,PERREF,PERURL \\
ECC\dotfill & Float & Orbital eccentricity & ECCUPPER,ECCLOWER,UECC,ECCREF,ECCURL \\
OM\dotfill & Float & Argument of periastron in degrees & OMUPPER,OMLOWER,UOM,OMREF,OMURL \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & KUPPER,KLOWER,UK,KREF,KURL \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & T0UPPER,T0LOWER,UT0,T0REF,T0URL \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & DVDTUPPER,DVDTLOWER,UDVDT,DVDTREF,DVDTURL \\

@@

systems only ZZZ still true?) & IUPPER,ILOWER,UI,IREF,IURL \\

@@

function) in $M_{\rm Jup}$ & MSINIUPPER,MSINILOWER,UMSINI,MSINIREF,MSINIURL \\
A\dotfill & Float & Orbital semimajor axis in AU & AUPPER,ALOWER,UA,AREF,AURL \\
MASS\dotfill & & & MASSUPPER,MASSLOWER,UMASS,MASSREF,MASSURL \\
SEP\dotfill & & & SEPUPPER,SEPLOWER,USEP,SEPREF,SEPURL \\

@@

LAMBDA\dotfill & Float & Projected spin-orbit misalignment & LAMBDAUPPER,LAMBDALOWER,ULAMBDA,LAMBDAREF,LAMBDAURL \\
BIGOM\dotfill & & & BIGOMUPPER,BIGOMLOWER,UBIGOM,BIGOMREF,BIGOMURL \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & DEPTHUPPER,DEPTHLOWER,UDEPTH,DEPTHREF,DEPTHURL \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & T14UPPER,T14LOWER,UT14,T14REF,T14URL \\

@@

HJD\tablenotemark{c} $-2,440,000$ & TTUPPER,TTLOWER,UTT,TTREF,TTURL \\
R\dotfill & Float & Radius of the planet in Jupiter radii & RUPPER,RLOWER,UR,RREF,RURL \\
AR\dotfill & $(a/R_*)$ & & ARUPPER,ARLOWER,UAR,ARREF,ARURL \\
B\dotfill & Float & Impact parameter of transit & BUPPER,BLOWER,UB,BREF,BURL \\

@@

DENSITYUPPER,DENSITYLOWER,UDENSITY,DENSITYREF,DENSITYURL \\

@@

GRAVITYUPPER,GRAVITYLOWER,UGRAVITY,GRAVITYREF,GRAVITYURL \\

@@

DR\dotfill & & & DRUPPER,DRLOWER,UDR,DRREF,DRURL \\
RR\dotfill & & & RRUPPER,RRLOWER,URR,RRREF,RRURL \\

@@

SE\dotfill & & & SEREF,SEURL \\

@@

SEDEPTHJUPPER,SEDEPTHJLOWER,USEDEPTHJ,SEDEPTHJREF,SEDEPTHJURL \\

@@

SEDEPTHHUPPER,SEDEPTHHLOWER,USEDEPTHH,SEDEPTHHREF,SEDEPTHHURL \\

@@

SEDEPTHKSUPPER,SEDEPTHKSLOWER,USEDEPTHKS,SEDEPTHKSREF,SEDEPTHKSURL \\

@@

SEDEPTHKPUPPER,SEDEPTHKPLOWER,USEDEPTHKP,SEDEPTHKPREF,SEDEPTHKPURL \\

@@

SEDEPTH36UPPER,SEDEPTH36LOWER,USEDEPTH36,SEDEPTH36REF,SEDEPTH36URL \\

@@

SEDEPTH45UPPER,SEDEPTH45LOWER,USEDEPTH45,SEDEPTH45REF,SEDEPTH45URL \\

@@

SEDEPTH58UPPER,SEDEPTH58LOWER,USEDEPTH58,SEDEPTH58REF,SEDEPTH58URL \\

@@

SEDEPTH80UPPER,SEDEPTH80LOWER,USEDEPTH80,SEDEPTH80REF,SEDEPTH80URL \\
SET\dotfill & & & SETUPPER,SETLOWER,USET,SETREF,SETURL \\

@@

MSTAR\dotfill & Float & Mass of host star & MSTARUPPER,MSTARLOWER,UMSTAR,MSTARREF,MSTARURL \\
RSTAR\dotfill & & & RSTARUPPER,RSTARLOWER,URSTAR,RSTARREF,RSTARURL \\
TEFF\dotfill & Float & Effective temperature of host star & TEFFUPPER,TEFFLOWER,UTEFF,TEFFREF,TEFFURL \\

@@

RHOSTARUPPER,RHOSTARLOWER,URHOSTAR,RHOSTARREF,RHOSTARURL \\

@@

host star & LOGGUPPER,LOGGLOWER,ULOGG,LOGGREF,LOGGURL \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & FEUPPER,FELOWER,UFE,FEREF,FEURL \\

>>>>

\tablecaption{Fields of Exoplanet Orbit Database\label{tab:par}}

@@

%

@@

BINARY\dotfill & Boolean & Star known ot be binary? & -REF, -URL \\

@@

V\dotfill & Float & $V$ magnitude & -REF,-URL \\

@@

DIST\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
PAR\dotfill & Float & Parallax in mas & -UPPER,-LOWER,U- \\

@@

star & -UPPER,-LOWER,U-,-REF,-URL \\
GAMMA\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
%

@@

PER\dotfill & Double & Orbital period in days & -UP-,-LOWER,U-,-REF,-URL \\
ECC\dotfill & Float & Orbital eccentricity & -UPPER,-LOWER,U-,-REF,-URL \\
OM\dotfill & Float & Argument of periastron in degrees & -UPPER,-LOWER,U-,-REF,-URL \\
K\dotfill & Float & Semiamplitude of stellar reflex motion in \mps & -UPPER,-LOWER,U-,-REF,-URL \\
T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
DVDT\dotfill & Float & Magnitude of linear trend in \mps\ day$^{-1}$ & -UPPER,-LOWER,U-,-REF,-URL \\

@@

systems only ZZZ still true?) & -UPPER,-LOWER,U-,-REF,-URL \\

@@

function) in $M_{\rm Jup}$ & -UPPER,-LOWER,U-,-REF,-URL \\
A\dotfill & Float & Orbital semimajor axis in AU & -UPPER,-LOWER,U-,-REF,-URL \\
MASS\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
SEP\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

LAMBDA\dotfill & Float & Projected spin-orbit misalignment & -UPPER,-LOWER,U-,-REF,-URL \\
BIGOM\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER,-LOWER,U-,-REF,-URL \\
T14\dotfill & Float & Time of transit from first to fourth contact in days & -UPPER,-LOWER,U-,-REF,-URL \\

@@

HJD\tablenotemark{c} $-2,440,000$ & -UPPER,-LOWER,U-,-REF,-URL \\
R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPE-,-LOWE-,U-,-REF,-URL \\
AR\dotfill & $(a/R_*)$ & & -UPPER,-LOWER,U-,-REF,-URL \\
B\dotfill & Float & Impact parameter of transit & -UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

DR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
RR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
%

@@

SE\dotfill & & & -REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\
SET\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\

@@

MSTAR\dotfill & Float & Mass of host star & -UPPER,-LOWER,U-,-REF,-URL \\
RSTAR\dotfill & & & -UPPER,-LOWER,U-,-REF,-URL \\
TEFF\dotfill & Float & Effective temperature of host star & -UPPER,-LOWER,U-,-REF,-URL \\

@@

-UPPER,-LOWER,U-,-REF,-URL \\

@@

host star & -UPPER,-LOWER,U-,-REF,-URL \\
FE\dotfill & Float & Iron abundance (or metallicity) of star & -UPPER,-LOWER,U-,-REF,-URL \\
